### 2012-11-25 paper.tex
forgot to delimit columns for two tables

With default settings, a random forest gains an accuracy on the census income data set that can be seen in table \ref{tab:adult:rand:default}:
\begin{table*}[b]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
                TP Rate  FP Rate  Precision  Recall  F-Measure  Class
                0.615    0.108    0.644      0.615   0.629      >50K
                0.892    0.385    0.88       0.892   0.886      <=50K
Weighted Avg.   0.825    0.318    0.823      0.825   0.824     
    \end{tabular*}
\caption{Random Forest -- Default Settings} 
\label{tab:adult:rand:default}
\end{table*}
which is surprisingly worse than the J48 algorithm.

@@

\begin{table*}[b]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
                TP Rate  FP Rate  Precision  Recall  F-Measure  Class
                0.606    0.064    0.749      0.606   0.67       >50K
                0.936    0.394    0.882      0.936   0.908      <=50K
Weighted Avg.   0.856    0.314    0.85       0.856   0.851     
    \end{tabular*}
\caption{Random Forest -- 7 Random Trees} 
\label{tab:adult:rand:7t}
\end{table*}
We can push the accuracy even further, if we take more random trees, e.g. twenty:
\begin{table*}[b]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
                & TP Rate  & FP Rate  & Precision &  Recall &  F-Measure  & Class  \\  \midrule          
                & 0.593    & 0.058    & 0.763     &  0.593  &  0.667      & >50K   \\     
                & 0.942    & 0.407    & 0.879     &  0.942  &  0.909      & <=50K  \\     
Weighted Avg.   & 0.858    & 0.323    & 0.851     &  0.858  &  0.851      &        \\  \bottomrule
    \end{tabular*}
\caption{Random Forest -- 20 Random Trees} 
\label{tab:adult:rand:20t}
\end{table*}

>>>>

With default settings, a random forest gains an accuracy on the census income data set that can be seen in table \ref{tab:adult:rand:default}:
\begin{table*}[b]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
              &  TP Rate & FP Rate & Precision & Recall & F-Measure & Class    \\  \midrule
              &  0.615   & 0.108   & 0.644     & 0.615  & 0.629     & >50K     \\     
              &  0.892   & 0.385   & 0.88      & 0.892  & 0.886     & <=50K    \\ 
Weighted Avg. &  0.825   & 0.318   & 0.823     & 0.825  & 0.824     &          \\ \bottomrule
    \end{tabular*}
\caption{Random Forest -- Default Settings} 
\label{tab:adult:rand:default}
\end{table*}
which is surprisingly worse than the J48 algorithm.

@@

\begin{table*}[b]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
              &  TP Rate & FP Rate & Precision & Recall & F-Measure & Class    \\  \midrule
              &  0.606   & 0.064   & 0.749     & 0.606  & 0.67      & >50K     \\ 
              &  0.936   & 0.394   & 0.882     & 0.936  & 0.908     & <=50K    \\ 
Weighted Avg. &  0.856   & 0.314   & 0.85      & 0.856  & 0.851     &          \\  \bottomrule
    \end{tabular*}
\caption{Random Forest -- 7 Random Trees} 
\label{tab:adult:rand:7t}
\end{table*}
We can push the accuracy even further, if we take more random trees, e.g. twenty:
\begin{table*}[b]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
                & TP Rate  & FP Rate  & Precision &  Recall &  F-Measure  & Class  \\  \midrule          
                & 0.593    & 0.058    & 0.763     &  0.593  &  0.667      & >50K   \\     
                & 0.942    & 0.407    & 0.879     &  0.942  &  0.909      & <=50K  \\     
Weighted Avg.   & 0.858    & 0.323    & 0.851     &  0.858  &  0.851      &        \\  \bottomrule
    \end{tabular*}
\caption{Random Forest -- 20 Random Trees} 
\label{tab:adult:rand:20t}
\end{table*}
